---
title: "Application 4: comparing redistricting scenarios"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 4: comparing redistricting scenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

`sim_redistrict()` calculates model predictions as the minority electorate share
changes from 1 to 100 percent in 0.1-point increments. Each returned vector has
991 values. Give each scenario a named column, then pass the resulting matrix to
`plot_redistrict()`.

```{r redistricting-scenarios, fig.width = 7, fig.height = 5}
plan_1 <- sim_redistrict(coethnic = 0.9, crossover = 0)
plan_2 <- sim_redistrict(coethnic = 0.9, crossover = 0.3)
plan_3 <- sim_redistrict(coethnic = 0.9, crossover = 0.5)

plans <- cbind(
  "No crossover" = plan_1,
  "Moderate crossover" = plan_2,
  "High crossover" = plan_3
)

plot_redistrict(plans = plans, range = c(44, 55))
```

`range` is expressed in electorate percentages, not vector positions. The plot
uses column names in its legend and can compare one or more scenarios. Choose
coethnic and crossover assumptions that are appropriate to the setting, then
compare how they change the relationship between electorate composition and
predicted success.
