---
title: "Application 4: comparing redistricting scenarios"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 4: comparing redistricting scenarios}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

## Motivating example: two proposed districts (Online Appendix C.2)

[Online Appendix C.2 of Atsusaka (2021)](https://static.cambridge.org/content/id/urn:cambridge.org:id:article:S000305542100054X/resource/name/S000305542100054Xsup001.pdf#page=19)
compares two proposed Louisiana districts with minority shares of 59.2% and
63.2%. It assumes all minority voters support the minority candidate, no White
voters do so, and minority and White turnout rates are 50% and 60%, respectively.
Under these assumptions, both plans yield probabilities very close to one, so
the additional four percentage points make little difference to the prediction.

```{r appendix-c2-districts}
appendix_C <- seq(from = 1, to = 100, by = 0.1)
louisiana_plan <- sim_redistrict(
  coethnic = 1, crossover = 0, gap = c(0.5, 0.6)
)
proposed_C <- c(59.2, 63.2)
proposed_index <- vapply(
  proposed_C, function(value) which.min(abs(appendix_C - value)), integer(1)
)
data.frame(
  minority_share = proposed_C,
  predicted_probability = louisiana_plan[proposed_index]
)
```

`sim_redistrict()` and `plot_redistrict()` let users examine the composition
range where a change would matter under their own assumptions. These are
conditional model predictions; comparisons of district plans do not by
themselves establish legal vote dilution.

## Comparing voting scenarios

`sim_redistrict()` calculates model predictions as the minority electorate share
changes from 1 to 100 percent in 0.1-point increments. Each returned vector has
991 values. Give each scenario a named column, then pass the resulting matrix to
`plot_redistrict()`.

```{r redistricting-scenarios, fig.width = 7, fig.height = 5}
plan_1 <- sim_redistrict(coethnic = 0.9, crossover = 0)
plan_2 <- sim_redistrict(coethnic = 0.9, crossover = 0.3)
plan_3 <- sim_redistrict(coethnic = 0.9, crossover = 0.5)

plans <- cbind(
  "No crossover" = plan_1,
  "Moderate crossover" = plan_2,
  "High crossover" = plan_3
)

plot_redistrict(plans = plans, range = c(44, 55))
```

`range` is expressed in electorate percentages, not vector positions. The plot
uses column names in its legend and can compare one or more scenarios. Choose
coethnic and crossover assumptions that are appropriate to the setting, then
compare how they change the relationship between electorate composition and
predicted success.
