---
title: "Application 5: finding a scenario's sweet spot"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 5: finding a scenario's sweet spot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

The sweet spot is the first minority electorate percentage at which a simulated
scenario reaches a chosen probability threshold. Use `plot_sweetspot()` to
display it alongside a district of interest.

```{r sweet-spot, fig.width = 7, fig.height = 5}
plan <- sim_redistrict(coethnic = 0.9, crossover = 0.2)

plot_sweetspot(
  plan = plan,
  threshold = 0.8,
  range = c(30, 70),
  C.prime = 70
)
```

`threshold` is a probability from 0 to 1. `C.prime` marks the minority
electorate percentage for a district of interest and must be within the plotted
`range`. If it is below the sweet spot, the plot represents a shortfall from the
chosen threshold; if it is above, it represents a surplus. Omitting `C.prime`
places it at the calculated sweet spot.

The sweet spot is conditional on the plan and the voting assumptions supplied to
`sim_redistrict()`. It is therefore a comparison tool, rather than a universal
electoral threshold.
