---
title: "Application 5: finding a scenario's sweet spot"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 5: finding a scenario's sweet spot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

## Motivating example: a sufficient minority share (Online Appendix C.3)

A 50% chance of electing a minority candidate and near certainty are different
targets. [Online Appendix C.3 of Atsusaka (2021)](https://static.cambridge.org/content/id/urn:cambridge.org:id:article:S000305542100054X/resource/name/S000305542100054Xsup001.pdf#page=20)
assumes all minority voters support the minority candidate, 30% of White voters
do so, and minority and White turnout rates are 40% and 50%, respectively. On
the package's 0.1-point grid, the prediction first reaches 50% at a minority
share of 47.6%; at 57%, it is approximately 100% at numerical precision.

```{r appendix-c3-threshold}
appendix_C <- seq(from = 1, to = 100, by = 0.1)
appendix_plan <- sim_redistrict(
  coethnic = 1, crossover = 0.3, gap = c(0.4, 0.5)
)
appendix_C[which(appendix_plan >= 0.5)[1]]
appendix_plan[which.min(abs(appendix_C - 57))]
```

This is conditional near certainty, rather than an electoral guarantee.
`plot_sweetspot()` identifies the share needed for a chosen `threshold`;
`C.prime` marks the district being compared with that threshold. Comparisons of
district plans do not by themselves establish legal vote dilution.

## Plotting a chosen threshold

The sweet spot is the first minority electorate percentage at which a simulated
scenario reaches a chosen probability threshold. Use `plot_sweetspot()` to
display it alongside a district of interest.

```{r sweet-spot, fig.width = 7, fig.height = 5}
plan <- sim_redistrict(coethnic = 0.9, crossover = 0.2)

plot_sweetspot(
  plan = plan,
  threshold = 0.8,
  range = c(30, 70),
  C.prime = 70
)
```

`threshold` is a probability from 0 to 1. `C.prime` marks the minority
electorate percentage for a district of interest and must be within the plotted
`range`. If it is below the sweet spot, the plot represents a shortfall from the
chosen threshold; if it is above, it represents a surplus. Omitting `C.prime`
places it at the calculated sweet spot.

The sweet spot is conditional on the plan and the voting assumptions supplied to
`sim_redistrict()`. It is therefore a comparison tool, rather than a universal
electoral threshold.
