---
title: "Application 1: district-level predictions"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 1: district-level predictions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

Use `minorep()` when the adjusted racial margin of victory (`M`) and minority
electorate share (`C`) are known for one or more districts. Both are percentages
from 0 to 100.

```{r district-predictions}
M <- c(20, 50, 30)
C <- c(40, 70, 85)

prediction <- minorep(M = M, C = C)
round(prediction, digits = 4)
```

The result contains one probability per district. `minorep()` returns
full-precision values, so retain `prediction` rather than its rounded display for
later analysis.

## Adjusting for turnout differences

If the minority and White turnout rates are 0.5 and 0.6, respectively, provide
them in that order with `gap`. Rates are proportions, not percentages.

```{r turnout-adjustment}
prediction_with_gap <- minorep(
  M = M,
  C = C,
  gap = c(0.5, 0.6)
)
round(prediction_with_gap, digits = 4)
```

The adjustment changes the effective minority share of the electorate before the
model calculates the probability. Use turnout rates that match the election or
scenario under study.
