---
title: "Application 1: district-level predictions"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 1: district-level predictions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

Use `minorep()` when the adjusted racial margin of victory (`M`) and minority
electorate share (`C`) are known for one or more districts. Both are percentages
from 0 to 100.

## Motivating example: influence districts (Online Appendix C.1)

Louisiana redistricting disputes raised the question of whether districts with
about 20% minority voters could elect minority candidates under strongly
polarized voting. The scenario in [Online Appendix C.1 of Atsusaka (2021)](https://static.cambridge.org/content/id/urn:cambridge.org:id:article:S000305542100054X/resource/name/S000305542100054Xsup001.pdf#page=18)
predicts a probability close to zero under those voting assumptions.

A second example considers a district with 40% minority voters. Assuming all
minority voters support the minority candidate and 30% of White voters do so,
`sim_M()` gives `M = 58`. Holding that margin fixed, `minorep()` predicts about a
3.3% chance with equal turnout, about 91.1% when minority turnout is 50% and
White turnout is 40%, and almost zero when those turnout rates are reversed.

```{r appendix-c1-influence}
influence_M <- sim_M(C = 40, coethnic = 1, crossover = 0.3)
influence_predictions <- c(
  "Equal turnout" = minorep(M = influence_M, C = 40),
  "Higher minority turnout" = minorep(
    M = influence_M, C = 40, gap = c(0.5, 0.4)
  ),
  "Lower minority turnout" = minorep(
    M = influence_M, C = 40, gap = c(0.4, 0.5)
  )
)
round(influence_predictions, digits = 4)
```

The same district composition can therefore produce very different predictions.
This comparison holds past performance (`M`) fixed while changing turnout in the
election being predicted. All probabilities are conditional on the supplied
assumptions, and this comparison alone does not establish legal vote dilution.
See [Application 2](application-2-racial-margin.html) for constructing `M`.

## Predicting several districts

```{r district-predictions}
M <- c(20, 50, 30)
C <- c(40, 70, 85)

prediction <- minorep(M = M, C = C)
round(prediction, digits = 4)
```

The result contains one probability per district. `minorep()` returns
full-precision values, so retain `prediction` rather than its rounded display for
later analysis.

## Adjusting for turnout differences

If the minority and White turnout rates are 0.5 and 0.6, respectively, provide
them in that order with `gap`. Rates are proportions, not percentages.

```{r turnout-adjustment}
prediction_with_gap <- minorep(
  M = M,
  C = C,
  gap = c(0.5, 0.6)
)
round(prediction_with_gap, digits = 4)
```

The adjustment changes the effective minority share of the electorate before the
model calculates the probability. Use turnout rates that match the election or
scenario under study.
