---
title: "Application 3: jurisdiction-level counts"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 3: jurisdiction-level counts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

`n_minorep()` converts district-level probabilities into simulated counts of
minority officeholders across a jurisdiction. It makes independent Bernoulli
draws for each district in every simulation.

```{r jurisdiction-counts}
district_M <- c(50, 40, 40, 35, 70, 85)
district_C <- c(50, 40, 60, 30, 50, 80)
district_prediction <- minorep(M = district_M, C = district_C)

count_draws <- n_minorep(
  model_pred = district_prediction,
  n_sim = 1000,
  seed = 2026
)
summary(count_draws)
```

`n_sim` controls the number of returned draws. Supplying `seed` makes the result
reproducible without changing the caller's random-number state.

## Inspect the simulation distribution

```{r count-histogram, fig.width = 7, fig.height = 4}
hist(
  count_draws,
  xlab = "Simulated number of minority officeholders",
  main = ""
)
```

The distribution represents uncertainty implied by the supplied district-level
probabilities. It should be interpreted alongside the assumptions used to
construct those probabilities.
