---
title: "Application 3: jurisdiction-level counts"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 3: jurisdiction-level counts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

## Motivating example: at-large versus district elections (Online Appendix C.4)

[Online Appendix C.4 of Atsusaka (2021)](https://static.cambridge.org/content/id/urn:cambridge.org:id:article:S000305542100054X/resource/name/S000305542100054Xsup001.pdf#page=21)
considers a jurisdiction with six seats and a jurisdiction-wide minority share
of 47.5%. It compares an at-large arrangement with six single-member districts
whose minority shares are `c(50, 40, 60, 30, 50, 80)` and whose adjusted racial
margins are `c(30, 40, 50, 65, 70, 30)`. Under this hypothetical comparison,
the simulations concentrate on zero minority officeholders at large and two
or three under district elections.

`minorep()` supplies the seat-level probabilities and `n_minorep()` converts
them into a distribution of counts, using independent draws across seats.
The district component can be reproduced directly from the appendix inputs:

```{r appendix-c4-district-counts}
appendix_M <- c(30, 40, 50, 65, 70, 30)
appendix_C <- c(50, 40, 60, 30, 50, 80)
appendix_prediction <- minorep(M = appendix_M, C = appendix_C)
appendix_counts <- n_minorep(
  model_pred = appendix_prediction, n_sim = 1000, seed = 2026
)
prop.table(table(appendix_counts))
```

The electoral-rule comparison is conditional on the voting assumptions and
the independence of seat outcomes. It does not by itself establish legal
vote dilution. The example below illustrates the same workflow with a different
set of district margins.

## Simulating jurisdiction totals

`n_minorep()` converts district-level probabilities into simulated counts of
minority officeholders across a jurisdiction. It makes independent Bernoulli
draws for each district in every simulation.

```{r jurisdiction-counts}
district_M <- c(50, 40, 40, 35, 70, 85)
district_C <- c(50, 40, 60, 30, 50, 80)
district_prediction <- minorep(M = district_M, C = district_C)

count_draws <- n_minorep(
  model_pred = district_prediction,
  n_sim = 1000,
  seed = 2026
)
summary(count_draws)
```

`n_sim` controls the number of returned draws. Supplying `seed` makes the result
reproducible without changing the caller's random-number state.

## Inspect the simulation distribution

```{r count-histogram, fig.width = 7, fig.height = 4}
hist(
  count_draws,
  xlab = "Simulated number of minority officeholders",
  main = ""
)
```

The distribution represents uncertainty implied by the supplied district-level
probabilities. It should be interpreted alongside the assumptions used to
construct those probabilities.
