---
title: "Application 2: calculating and simulating the racial margin"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Application 2: calculating and simulating the racial margin}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

The adjusted racial margin of victory, `M`, can come from observed election
returns or from a prospective voting scenario. This vignette demonstrates both
paths.

## Calculate `M` from observed vote shares

`comp_M()` accepts the vote shares, on a 0–100 scale, of the top minority and
top White candidates.

```{r observed-margin}
top_minority <- c(18, 40, 85, 20)
top_white <- c(60, 40, 10, 34)

observed_M <- comp_M(Vm = top_minority, Vw = top_white)
observed_M
```

Pass the resulting margins to `minorep()` with the corresponding electorate
shares to make predictions.

## Simulate `M` from voting assumptions

For a prospective scenario, `sim_M()` derives `M` from the minority electorate
share, coethnic voting, and White crossover voting. `coethnic` is the share of
minority voters expected to support the minority candidate; `crossover` is the
analogous White-voter share. Both are proportions from 0 to 1.

```{r simulated-margin}
hypothetical_C <- c(40, 50, 60)
simulated_M <- sim_M(
  C = hypothetical_C,
  coethnic = 1,
  crossover = 0.3
)
simulated_M

round(minorep(M = simulated_M, C = hypothetical_C), digits = 4)
```

These assumptions should be explicit and substantively defensible. Varying them
is often a useful way to understand how a scenario depends on voting behavior.
