---
title: "Overview of logical"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Overview of logical}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

`logical` produces quantitative predictions from the logical model of minority
representation developed in Atsusaka (2021). The model describes the probability
that a minority candidate emerges and wins in a district. It is a tool for
examining observed elections and explicit scenarios; the article's validation
results describe its evaluated samples, not a guaranteed accuracy rate for every
new election or district plan.

## What are logical models?

A logical model begins with a transparent account of the conditions that make an
outcome possible. Here, candidate emergence and electoral success depend on two
district-level quantities: the electoral environment facing a minority candidate
and the minority share of the electorate. The package turns those quantities and
clearly stated assumptions into probabilities, simulations, and visual
comparisons. It does not replace substantive knowledge about local candidates,
institutions, or elections.

The core inputs are:

- `M`, the adjusted racial margin of victory based on a previous election, on a
  0–100 scale;
- `C`, the minority share of the electorate, on a 0–100 scale;
- optional turnout rates, coethnic voting, and White crossover voting, each on a
  0–1 scale.

## The vignette series

The next vignette, [Theory](theory.html), explains the logical model and its
quantities. The five application vignettes then demonstrate how to:

1. make district-level predictions;
2. calculate or simulate `M`;
3. simulate jurisdiction-level counts;
4. compare redistricting scenarios; and
5. find a scenario's sweet spot.

The package also includes the Louisiana mayoral and state legislative datasets
used to evaluate the model. Load `louisiana` or `state_legislative` with
`data()` and consult `?louisiana` or `?state_legislative` for their codebooks.

## A first prediction

For a district with `M = 50` and `C = 70`, calculate the probability of minority
candidate emergence and electoral success as follows:

```{r first-prediction}
minorep(M = 50, C = 70)
```

`minorep()` returns a full-precision probability. Round it only when presenting
the result in a table, figure, or narrative.

## Reference

> Atsusaka, Yuki. 2021. “A Logical Model for Predicting Minority
> Representation: Application to Redistricting and Voting Rights Cases.”
> *American Political Science Review* 115 (4): 1210–1225.
> <https://doi.org/10.1017/S000305542100054X>
