---
title: "Overview: Computing and Visualizing Quantitative Predictions of Logical Models"
author: "Yuki Atsusaka and Kolbe A. Dumas"
output:
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Overview: Computing and Visualizing Quantitative Predictions of Logical Models}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(logical)
```

**This R package is for computing and visualizing the quantitative predictions
of a logical model of minority representation.** This quantitatively predictive
logical model was developed in Atsusaka (2021), [“A Logical Model for Predicting
Minority Representation: Application to Redistricting and Voting Rights
Cases”](https://doi.org/10.1017/S000305542100054X), *American Political Science
Review* 115(4): 1210–1225.

For quantitatively predictive logical models more generally, please refer to:

- Taagepera, Rein. 2007. [*Predicting Party Sizes: The Logic of Simple
  Electoral Systems*](https://books.google.com/books?id=T_YTDAAAQBAJ&printsec=frontcover&dq=rein+taagepera#v=onepage&q=rein%20taagepera&f=false).
  Oxford University Press.
- Taagepera, Rein. 2008. [*Making Social Sciences More Scientific: The Need for
  Predictive Models*](https://books.google.com/books?id=l6tiJLcVZ8AC&printsec=frontcover&dq=rein+taagepera#v=onepage&q=rein%20taagepera&f=false).
  Oxford University Press.
- Shugart, Matthew S., and Rein Taagepera. 2017. [*Votes from Seats: Logical
  Models of Electoral Systems*](https://books.google.com/books?id=0S42DwAAQBAJ&printsec=frontcover&dq=rein+taagepera#v=onepage&q=rein%20taagepera&f=false).
  Cambridge University Press.

## What are logical models?

The logical model of minority representation is a simple mathematical formula
introduced in Atsusaka (2021). Its purpose is to explain and predict when
minority candidates run for office and win electoral contests. In the Louisiana
mayoral and state legislative samples evaluated in the article, the model
correctly predicts over 90% of minority candidate emergence and over 95% of
minority electoral success; these results do not guarantee the same accuracy in
every new election or district plan.

The model states that the probability that a minority candidate runs for office
in a district is equal to the estimated probability that the candidate can win
the election. This probability is represented by the standard normal cumulative
distribution function of the square root of a product of two terms (`M` and
`C`), minus 50:

\[
\Pr(\text{Minority Runs}) = \Pr(\text{Minority Wins}) =
\Phi\left(\sqrt{MC} - 50\right).
\]

Here:

- `C` is the percentage of minority voters in the electorate. In the presence
  of extreme racial polarization, `C` represents the racial margin of victory.
- `M` is the adjusted racial margin of victory in the most recent election,
  calculated as `(Vt-1M - Vt-1W) / 2 + 50`, where `Vt-1M` and `Vt-1W` are the
  vote shares of the top minority and White candidates, respectively. `M`
  represents past minority-candidate performance relative to White candidates
  and how securely minority candidates obtain descriptive representation.

The core idea of the model is that future minority-candidate performance falls
between the two logical bounds defined by `M` and `C`. At one extreme, upcoming
election results match the most recent election (`M`). At the other, they match
what district racial composition implies under perfect racially polarized voting
(`C`). The geometric mean, \(\sqrt{MC}\), expresses this middle position.

## The vignette series

The next vignette, [Theory](theory.html), explains the logical model and its
quantities. The five application vignettes then demonstrate how to:

1. make district-level predictions;
2. calculate or simulate `M`;
3. simulate jurisdiction-level counts;
4. compare redistricting scenarios; and
5. find a scenario's sweet spot.

The package also includes the Louisiana mayoral and state legislative datasets
used to evaluate the model. Load `louisiana` or `state_legislative` with
`data()` and consult `?louisiana` or `?state_legislative` for their codebooks.

## A first prediction

For a district with `M = 50` and `C = 70`, calculate the probability of minority
candidate emergence and electoral success as follows:

```{r first-prediction}
minorep(M = 50, C = 70)
```

`minorep()` returns a full-precision probability. Round it only when presenting
the result in a table, figure, or narrative.

## Reference

> Atsusaka, Yuki. 2021. “A Logical Model for Predicting Minority
> Representation: Application to Redistricting and Voting Rights Cases.”
> *American Political Science Review* 115 (4): 1210–1225.
> <https://doi.org/10.1017/S000305542100054X>
